Preliminary Thesis Defence

### 2013-11-22 draft.Rnw
corrections endnotes

I realise that almost of all the previously discussed research projects are some form of a replication of a prior work. As replications they are mostly critiques of others' work, rather than constructive idea. This is mostly a results of the fact that it is easier to progress when building upon the works of others. For this reason, these research projects have progressed more then the projects which are primarily based on my own ideas. However, it is my attention to shift the focus of my thesis to include more original work. Here I present two more ideas which are to premature to include in the main body of the text, but are based on my own work.

@@

Also, \parencite{taleb2010black, sornette2009dragon}

>>>>

I realise that almost of all the previously discussed research projects are some form of a replication of prior work. As replications they are mostly critiques of others' work, rather than constructive idea. This is mostly a results of the fact that it is easier to progress when building upon the works of others. For this reason, these research projects have progressed more then the projects which are primarily based on my own ideas. However, it is my attention to shift the focus of my thesis to include more original work. Here I present two more ideas which are to premature to include in the main body of the text, but are based on my own work.

@@

Lastly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy. I would like to write one paper about an issue relating to this. In particular I would like to at the effect of outliers. The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as indiviual behaviour \parencite{kahneman2011thinking}. I would like to see how these principles affect research in development microeconomics.
